---
output: github_document
bibliography: references.bib
format: gfm
---


<!-- README.md is generated from README.qmd. Please render that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

**NOTE: This is a R package created for reproducing my thesis.**



# inga

<!-- badges: start -->

<!-- badges: end -->

A R package for causal inference in survival analysis.The name "inga" comes from the Japanese word 「因果(いんが)」,which means cause and effect.

The goal of inga is to provide causal methods for survival analysis[@hernan] and reproduce the code from the book "First Course in Causal Inference".[@ding]

## Installation

You can install the development version of inga from [GitHub](https://github.com/sysukili/inga) with:

``` r
# install.packages("devtools")
devtools::install_github("sysukili/inga")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(inga)
## basic example code
```
